---
title: "Introduction to R"
author: "Catherine Holloway and Mine Dogucu"
date: "January 29, 2018"
output: ioslides_presentation
---

##Projects

+ Make a folder on your computer and name it R Ladies.
+ File > New Project > New Directory > New Project
Write Introduction to R as Directory Name and Browse to select the R Ladies folder. Cretae Project
+ File > New Script


##Opening Datasets

Download __North Carolina Births__ and __Gun Violence__ datasets from


https://www.openintro.org/stat/data/

Save these datasets in your Introduction to R folder. 

##Opening Datasets

```{r echo=FALSE}

nc <- read.csv("nc.csv")
#print(nc)
```


```{r eval=FALSE}
nc <- read.csv("Introduction to R/nc.csv")
print(nc)
```

##Summarizing datasets : str()

```{r}
str(nc)
```


##Summarizing datasets : head()

```{r}
head(nc)
```


##Summarizing datasets : tail()

```{r}
tail(nc)
```


##Descriptive Statisitics

```{r}
summary(nc)
```


##Selecting Variables

```{r}
mean(nc$mage)
```

##Arguments

Can you find mean age of fathers?

##Arguments

```{r}
mean(nc$fage)
```

##Arguments

```{r}
mean(nc$fage, na.rm=FALSE)
```

##Using R help

Let's assume we are interested interested in making a scatterplot to show the relationship between _mother's age and _mage_ and _weeks_ and we do not know how to do this yet. 


##Using R help
```{r eval=FALSE}
?plot
```


##Using R help

```{r}
plot(nc$mage, nc$weeks)
```

##Using R help

```{r}
plot(nc$mage, nc$weeks, xlab="Mother's age", ylab="Weeks")
```


##Practice

+ Open _gun_violence_ dataset and name your object _gun_
+ Look at the head and tail of the dataset as well as the summary
+ Make a plot to look at the relationship betwen _mortality_rate_, _ownership_rate_ 

##Practice 

```{r echo=FALSE}
gun<-read.csv("gun_violence.csv")
```


```{r}
plot(gun$ownership_rate, gun$mortality_rate, 
     xlab="Gun Ownership Rate", 
     ylab="Mortality Rate")
text(gun$ownership_rate,gun$mortality_rate, 
     labels= gun$country)
```


##Practice

```{r}
plot(gun$ownership_rate, gun$mortality_rate, 
     xlab="Gun Ownership Rate", ylab="Mortality Rate", 
     ylim=c(0,10))
text(gun$ownership_rate,gun$mortality_rate, 
     labels= gun$country)
```