---
title: "Data Visualization with ggplot2"
subtitle: R-Ladies Sarasota
author: "Mine Dogucu"
date: "March 26, 2018"
output: ioslides_presentation
---

## Setup

```{r message=FALSE, warning=FALSE}
library(tidyverse)
nc<-read_csv("nc.csv")
nc<-drop_na(nc)

```

# One Categorical Variable

## Plot 1

What kind of a graph is this?

```{r echo=FALSE}
ggplot(nc, aes(marital))+geom_bar()
```

## Step by Step Barplot 

```{r }
ggplot(nc)
```

## Step by Step Barplot 

```{r }
ggplot(nc,aes(x=marital))
```

## Step by Step Barplot 

```{r }
ggplot(nc)
```

## Step by Step Barplot 

```{r }
ggplot(nc, aes(x=marital))
```

## Step by Step Barplot 

```{r }
ggplot(nc,aes(x=marital))+
  geom_bar()
```

# Two Categorical Variables 

## Step by Step Barplot

```{r }
ggplot(nc,aes(x=marital, fill=whitemom))+
  geom_bar()
```

## Practice

```{r echo=FALSE}
ggplot(nc,aes(x=lowbirthweight, fill=premie))+
  geom_bar()
```

## Practice

```{r}
ggplot(nc,aes(x=lowbirthweight, fill=premie))+
  geom_bar()
```

# One Continuous Variable

## Plot 2

```{r echo=FALSE}
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1,        aes(fill=I('indianred2'),color=I('midnightblue')))
  
```

## Step by Step Histogram

```{r }
ggplot(nc)
  
```

## Step by Step Histogram

```{r }
ggplot(nc,aes(x=weight))
  
```

## Step by Step Histogram


```{r }
ggplot(nc,aes(x=weight))+
  geom_histogram()        
```

## Step by Step Histogram

```{r }
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1)
  
```

## Step by Step Histogram

```{r}
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1, aes())
  
```

## Step by Step Histogram

```{r}
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1, aes(fill=I('red')))
  
```


## Step by Step Histogram

```{r }
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1, aes(fill=I('indianred2')))
  
```

## Step by Step Histogram

```{r }
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1, 
                 aes(fill=I('indianred2')))
  
```

## Step by Step Histogram

```{r}
ggplot(nc,aes(x=weight))+
  geom_histogram(binwidth=1, 
                 aes(fill=I('indianred2'),
                     color=I('midnightblue')))
  
```


## Plot 3

What kind of a plot is this?

```{r echo=FALSE}
ggplot(nc,aes(x=weight, fill=habit))+
  geom_dotplot(binwidth = 0.14)
```

## Step by Step dotplots

```{r}
ggplot(nc)
```

## Step by Step dotplots

```{r}
ggplot(nc,aes(x=weight))
```

## Step by Step dotplots

```{r}
ggplot(nc,aes(x=weight))+
  geom_dotplot()
```

## Step by Step Dotplots

```{r}
ggplot(nc,aes(x=weight))+
  geom_dotplot(binwidth = 0.14)
```

## Step by Step Dotplots

```{r}
ggplot(nc,aes(x=weight, fill=habit))+
  geom_dotplot(binwidth = 0.13)
```

# One Continuous One Categorical Variable

## Plot 4

What kind of a plot is this?

```{r echo=FALSE}
ggplot(nc,aes(x=habit,y=weight))+
  geom_boxplot(aes(fill=I('chartreuse'),
                   color=I('lightslateblue')))
```

## Step by Step Boxplots

```{r}
ggplot(nc)

```

## Step by Step Boxplots

```{r}
ggplot(nc,aes(x=habit,y=weight))
```

## Step by Step Boxplots

```{r}
ggplot(nc,aes(x=habit,y=weight))+
  geom_boxplot()
```

## Step by Step Boxplots

```{r}
ggplot(nc,aes(x=habit,y=weight))+
  geom_boxplot(aes())
```

## Step by Step Boxplots

```{r}
ggplot(nc,aes(x=habit,y=weight))+
  geom_boxplot(aes(fill=I('chartreuse')))
```

## Step by Step Boxplots

```{r}
ggplot(nc,aes(x=habit,y=weight))+
  geom_boxplot(aes(fill=I('chartreuse'),
                   color=I('lightslateblue')))
```

# Two Continuous Variables 

## Plot 5

```{r echo=FALSE}
ggplot(nc, aes(x=gained, y=weight))+
  geom_point(shape=17)+
  facet_grid(habit~premie)
```

## Step by Step Scatterplots

```{r}
ggplot(nc)
```

## Step by Step Scatterplots

```{r}
ggplot(nc, aes(x=gained, y=weight))
```

## Step by Step Scatterplots

```{r}
ggplot(nc, aes(x=gained, y=weight))+
  geom_point()
```

## Step by Step Scatterplots

```{r}
ggplot(nc, aes(x=gained, y=weight))+
  geom_point(shape=17)
```

## Step by Step Scatterplots

```{r}
ggplot(nc, aes(x=gained, y=weight))+
  geom_point(shape=17)+
  facet_grid(habit~premie)
```



## Saving Plots

One way:

Plots> Export > Save as Image 

+ Select the directory you would like to save (ideal to save under figs).
+ Name the file to save.
+ Click Save

## Saving Plots

The other way:

```{r message=FALSE}
ggsave("myplot.png")
```



